---
output:
  reprex::reprex_document:
    venue: "gh"
    advertise: FALSE
    session_info: TRUE
    style: TRUE
    comment: "#;-)"
    tidyverse_quiet: FALSE
    std_out_err: TRUE
knit: reprex::reprex_render
---

This template demonstrates many of the bells and whistles of the `reprex::reprex_document()` output format. The YAML sets many options to non-default values, such as using `#;-)` as the comment in front of output.

## Code style

Apple Top International

```{r}
knitr::opts_chunk$set(echo = TRUE)
library("tidyverse")
library("dplyr")
library(tibble)

apple_Dfr <- read_csv("../websitedata/appletopsongsinternational2023.csv")
apple_Tibble <- as_tibble(apple_Dfr)

apple_Tibble <- apple_Tibble %>%
  pivot_longer(cols = c(-"Pos", -"P+", -"Artist and Title", -"Days",
  -"Pk", -"(x?)", -"Pts", -"Pts+", -"TPts"), names_to = "country", values_to = "country_rank")

apple_Tibble <- apple_Tibble %>%
  select(-"P+", -"(x?)", -"Pts+", -"TPts")

colnames(apple_Tibble) <- c("Chart Position", "Artist and Title", "Position Duration", 
"Peak", "Points", "Country", "Country Rank") 

#print(sum(is.na(loan_Tibble))) check missing values
dim(apple_Tibble)
head(apple_Tibble)
```

## Quiet tidyverse

Netflix Top 2022


```{r}
knitr::opts_chunk$set(echo = TRUE)
library("tidyverse")
library("dplyr")
library(tibble)

netflix_Dfr <- read_csv("../websitedata/netflixbestshows2022.csv")
netflix_Tibble <- as_tibble(netflix_Dfr)

colnames(netflix_Tibble) <- c("Title", "Release Year", "Score", "Votes (Amount)", "Duration", 
                                      "Total Seasons", "Main Genre", "Main Production")

#netflix_Tibble <- arrange(- netflix_Tibble$"Release Year")

#print(sum(is.na(netflix_Tibble))) for missing values
dim(netflix_Tibble)
head(netflix_Tibble)
```

## Chunks in languages other than R

Remember: knitr supports many other languages than R, so you can reprex bits of code in Python, Ruby, Julia, C++, SQL, and more. Note that, in many cases, this still requires that you have the relevant external interpreter installed.

Let's try Python!

```{python, eval = Sys.which("python") != "", python.reticulate = requireNamespace("reticulate", quietly = TRUE)}
x = 'hello, python world!'
print(x.split(' '))
```

